Evolution of Income Inequality in Canada

### 2022-05-05 outputs/paper.Rmd
fix grammar1

---
title: "Evolution of Income Inequality in Canada"
subtitle: "It's becoming a more serious issue as over time, especially in the richest provinces."
author: 
  - Alicia Yang
thanks: "Code and data are available at: https://github.com/Alicia-y/Telling-stories-with-data-final-paper"
date: "`r format(Sys.time(), '%d %B %Y')`"
abstract: "People have claimed that the income disparity in Canada has increased alongside with the rapid growth of its economy. To explore whether and how income disparity became a serious issue in Canada, this paper aims to investigate the relationship between time, province, and income inequality in Canada. By utilizing the data from Statistics Canada, we found that income inequality continuously increase over time and is a greater issue in more developed provinces. Particularly, it is closely related to the prosperity of a region. In addition, implications and possible reasons behind this correlation is discussed and possible solutions to the problem of income disparity is proposed."
output:
  bookdown::pdf_document2
toc: TRUE
bibliography: references.bib
---

>>>>

---
title: "Evolution of Income Inequality in Canada"
subtitle: "It's becoming a more serious issue over time, especially in the richest provinces."
author: 
  - Alicia Yang
thanks: "Code and data are available at: https://github.com/Alicia-y/Telling-stories-with-data-final-paper"
date: "`r format(Sys.time(), '%d %B %Y')`"
abstract: "People have claimed that the income disparity in Canada has increased alongside with the rapid growth of its economy. To explore whether and how income disparity became a serious issue in Canada, this paper aims to investigate the relationship between time, province, and income inequality in Canada. By utilizing the data from Statistics Canada, we found that income inequality continuously increase over time and is a greater issue in more developed provinces. Particularly, it is closely related to the prosperity of a region. In addition, implications and possible reasons behind this correlation is discussed and possible solutions to the problem of income disparity is proposed."
output:
  bookdown::pdf_document2
toc: TRUE
bibliography: references.bib
---
